Proof No Diamond (3 layers)

### 2024-01-15 Paper/proof revison.tex
update proof

\section{Theorem 2}

We now show that if all intermediates nodes that are on compensating pairs are opened as MILP nodes, then MILP will be correct. First, we do the proof with 3 layers, assuming (without loss of generality) a unique output node $z$.

\begin{theorem}
	\label{no_diamond_2}
	Using MILP method, if every nodes $b_j$ in any compensating path pair
	 $(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
	 bounds computed by MILP are the exact max and min value of $z$.
\end{theorem}

By symetry, we only show the max side.

\begin{definition}
	Let $K$ be the set of all input nodes $a_k$. 
	We define a decomposition $K=I\sqcup J$ as follows:  
	\begin{itemize}
 \item $k \in I$  if
 \begin{enumerate}
	 \item every path from $a_k$ to $z$ has weight $\geq 0$, or
	\item every path from $a_k$ to $z$ has weight $\leq 0$.
 \end{enumerate}
That is, $a_k$ is not a source of a compensating pair.
	\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
	one with positive and one with negative weight.
\end{itemize}
\end{definition}

\begin{lemma} \label{lem:open_node}
	A node $b$ in the hidden layer will not be on a compensating pair iff one of the following two happens:
	\begin{enumerate}
	 \item $w_{b,z}=0$, or
	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.
	\end{enumerate}
	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
\end{lemma}

\begin{proof}
	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.

	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
	Then $((a_j,b,z), \pi')$ is also a compensating pair.
\end{proof}

\begin{definition}\label{sign_of_nodes_in_I}
	We define a partial sign function $S$ over nodes $n$ such that : 	
	\begin{enumerate} 
		 \item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
		 \item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
		 \item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
		 \item Otherwise $S(n)$ is undefined.
	\end{enumerate}
\end{definition}

Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also). Hence it is undefined only for nodes $a_j$ with $j \in J$.

We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
Consider $\boldsymbol{x}_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).

\begin{lemma} \label{lem:reach_max}
	$max_a (weight_{a}(z)) = max_{\{a \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (weight_{a}(z))$

	Further, for every intermediate node $b$ in the hidden layer, for any valuation $\boldsymbol{x}^0_J$, 
	we have $max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (weight_{a}(b)) = max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J,\boldsymbol{x}_I=\boldsymbol{x}_I^*\}} (weight_{a}(b))$.	
\end{lemma}

\begin{proof}
	For the first statement, we use 
	$$max_{\boldsymbol{x}_K} (weight_{\boldsymbol{x}_K}(z)) = max_{\boldsymbol{x}_J} max_{\boldsymbol{x}_I} (weight_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$

	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers 
	as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.

	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
\end{proof}

Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
\begin{itemize}
	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
\end{itemize}

\begin{lemma}\label{lem:AppB=ReLU}
	Let $\mathrm{AppB}$ be the upper bound of lower bound approximation functions of LP for $\ReLU$ function with known upper and lower bound (numbers) $u,l$. Then when $x$ reaches the extremal values (maximum or minimum values, $u$ or $l$), then $\mathrm{AppB}(x)=\ReLU(x)$.

\begin{proof}
	This is simply by definition of LP approximation functions.
\end{proof}

Notice that there is only one layer of ReLUs, in the hidden layer.
Denote by $\mathrm{UB}$ the maximal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.

We want to show that $\mathrm{UB} = \max z$. As the MILP abstraction is a sound overapproximation, 
it suffices to show that $\mathrm{UB}\leq \max c$.

For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
$b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
$\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}$. We have:
%We show that this upper bound does not exceed the maximal value of $z$:

\begin{align*}
	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
of its (LP) approximation if $w_{b,z}<0$.

By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:

\begin{align*}
	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
\end{align*}

Added FIX:
Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.
Hence:

$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$

For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$
by definition of $B_{pure}$ (Lemma 4.), hence

$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
$weight_{\boldsymbol{x}^*_I}(b)$ is an extremal value (minimum or maximal) and 
$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.

Hence we have: \begin{align*}
	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
	\leq & \max_{\boldsymbol{x}_J}\max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\boldsymbol{x}_J) 	= \max_{\boldsymbol{x}_K} weight_{\boldsymbol{x}_K}(z)
\end{align*}

Considering the maximal over all inputs $\boldsymbol{x}_J,\boldsymbol{x}_I$, we obtain

$$\mathrm{UB} = max_{\boldsymbol{x}_J,\boldsymbol{x}_I} \mathrm{UB}_{\boldsymbol{x}_J,\boldsymbol{x}_I} \leq \max_{\boldsymbol{x}_J,\boldsymbol{x}_I} weight_{\boldsymbol{x}_J,\boldsymbol{x}_I}(z)$$ And this us what we want to show.

\section{Proof of Theorem 2, full version}

In this section, we will try to prove the full version of theorem 2, that is

@@

We uses very similar definitions as in previous section.

@@

	We denote $B_O$ the set of all nodes $b$ that is in a compensating path.
\end{lemma}

@@

	3. if $b\in B_{zero}$, then $w_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.

@@

\begin{proof}
	Otherwise, suppose there exists two paths $P_1,P_2$ from $b$ to $z$ with (strictly) different signs. Then consider $\langle a_i,b\rangle+P_1$ and $\langle a_i,b\rangle+P_2$, they are two paths with weights with different signs. This is a contradiction since $a_i\in I$.
\end{proof}
Therefore, for any node $b$  that $S$ is undefined on $b$, it is only depending on the values on $J$.

\begin{lemma}
	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$. Then $W_{bc}S(c)=S(b)$.
\end{lemma}

@@

We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$. We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$. We can see that for a node $b$ that $S$ is not defined on it, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ becomes a constant.

@@

	Now, for any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers 
	as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.

	For the second part, for any $b$ that is at least 2 layers after $a$, we can regard $b$ as the output node and apply the same argument above.

	If $b$ is immediately after $a$, then the proof is the same as last part of Lemma \ref{lem:reach_max} last section.

@@

	(2) If $S(c)=1$, then we have the following:	\begin{align*}
		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
	\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$. Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}\wedge w_{b,c}\neq 0} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
	= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
	\end{align*}  This is the first equal.

>>>>

%\section{Theorem 2}
%
%We now show that if all intermediates nodes that are on compensating pairs are opened as MILP nodes, then MILP will be correct. First, we do the proof with 3 layers, assuming (without loss of generality) a unique output node $z$.
%
%\begin{theorem}
%	\label{no_diamond_2}
%	Using MILP method, if every nodes $b_j$ in any compensating path pair
%	 $(\pi,\pi')$ is encoded as a binary/integer variable, then the upper and lower 
%	 bounds computed by MILP are the exact max and min value of $z$.
%\end{theorem}
%
%By symetry, we only show the max side. 
%
%
%
%\begin{definition}
%	Let $K$ be the set of all input nodes $a_k$. 
%	We define a decomposition $K=I\sqcup J$ as follows:  
%	\begin{itemize}
% \item $k \in I$  if
% \begin{enumerate}
%	 \item every path from $a_k$ to $z$ has weight $\geq 0$, or
%	\item every path from $a_k$ to $z$ has weight $\leq 0$.
% \end{enumerate}
%That is, $a_k$ is not a source of a compensating pair.
%	\item $k \in J$ if $k \notin I$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
%	one with positive and one with negative weight.
%\end{itemize}
%\end{definition} 
%
%
%\begin{lemma} \label{lem:open_node}
%	A node $b$ in the hidden layer will not be on a compensating pair iff one of the following two happens:
%	\begin{enumerate}
%	 \item $w_{b,z}=0$, or
%	 \item For every input node $j\in J$, we have $w_{a_j,b}=0$.
%	\end{enumerate}
%	We denote $B_{pure}$ the set of such nodes $b$ such that at least one of the above holds.
%\end{lemma}
%
%\begin{proof}
%	First, we show that if either one of 1,2 happens, then $b_i$ will not be opened. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of compensating paths 	$(\pi,\pi')$ starting with $a$, with $k$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $w_{a_j,b}=0$ implies weight$(\pi)=0$.
%	
%	Second, we show that if neither 1 nor 2 hold, then $b$ will be on a compensating path.
%	Because 2) does not hold, there is a $j \in J$ with $w_{a_j,b} \neq 0$, say $>0$.
%	Because 1) does not hold, $w_{b,z} \neq 0$, say $>0$.
%	Now, by definition of $J$, there is a pair of compensating paths $\pi,\pi'$ 
%	from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
%	Then $((a_j,b,z), \pi')$ is also a compensating pair.
%\end{proof}
%
%Consider the sign of nodes function from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, we cannot define this function over all nodes.
%
%
%\begin{definition}\label{sign_of_nodes_in_I}
%	We define a partial sign function $S$ over nodes $n$ such that : 	
%	\begin{enumerate} 
%		 \item all paths from $n$ to $z$ have 0 weight, and then $S(n)=0$; 
%		 \item all paths from $n$ to $z$ have non-negative weight, and at least one path has a positive weight, and then $S(n)=1$; 
%		 \item all path from $n$ to $z$ has non-positive weight, and at least one path has a negative weight, and then $S(n)=-1$.
%		 \item Otherwise $S(n)$ is undefined.
%	\end{enumerate}
%\end{definition}	
%	
%Notice that $S$ is defined on all nodes $a_i$ with $i \in I$ (it can also be defined trivially for all nodes $b$ as there is a unique path to $z$, and at $z$ also). Hence it is undefined only for nodes $a_j$ with $j \in J$.
%
%
%We denote $a_S$ for any subset $S\subseteq K$ to refer the input vector $\langle a_k\rangle_{a_k\in S}$. We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$.
%Consider $\boldsymbol{x}_I^*$ the input vector such that for all $i \in I$, the value for $a_i$ gets its maximal value (if $S(a_i)=1$) or $a_i$ gets its minimal value (if $S(a_i)=-1$).
%
%\begin{lemma} \label{lem:reach_max}
%	$max_a (weight_{a}(z)) = max_{\{a \mid \boldsymbol{x}_I=\boldsymbol{x}^*_I\}} (weight_{a}(z))$
%	
%	Further, for every intermediate node $b$ in the hidden layer, for any valuation $\boldsymbol{x}^0_J$, 
%	we have $max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J\}} (weight_{a}(b)) = max_{\{a \mid \boldsymbol{x}_J=\boldsymbol{x}^0_J,\boldsymbol{x}_I=\boldsymbol{x}_I^*\}} (weight_{a}(b))$.	
%\end{lemma}
%
%\begin{proof}
%	For the first statement, we use 
%	$$max_{\boldsymbol{x}_K} (weight_{\boldsymbol{x}_K}(z)) = max_{\boldsymbol{x}_J} max_{\boldsymbol{x}_I} (weight_{\boldsymbol{x}_I,\boldsymbol{x}_J}(z))$$
%	
%	Now, for any fixed input $\boldsymbol{x}^0_J$, we can regard $weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers 
%	as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} (make a more precise corollary) to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
%	
%	The second statement is simpler because for each fixed partial input $\boldsymbol{x}^0_J$, 
%	$$b= B^0 +\sum_{a_i\in I} w_{a_i, b} a_i,$$ where $B^0$ is a constant which is the sum of the term including bias and $\boldsymbol{x}^0_J$. Applying Lemma \ref{lemma1}, we obtain the statement.
%\end{proof}
%
%\subsection{MILP abstraction}
%
%Consider now an MILP abstraction using the abstraction from \cite{MILP}, 
%where each variable $\alpha_b$ for the ReLU from $b^-$ to $b^+$ is:
%\begin{itemize}
%	\item linear  (i.e. $\alpha_b \in [0,1]$) for $b \in B_{pure}$
%	\item binary/integer (i.e. $\alpha_b \in \{0,1\}$) for $b \notin B_{pure}$
%\end{itemize}
%
%
%\begin{lemma}\label{lem:AppB=ReLU}
%	Let $\mathrm{AppB}$ be the upper bound of lower bound approximation functions of LP for $\ReLU$ function with known upper and lower bound (numbers) $u,l$. Then when $x$ reaches the extremal values (maximum or minimum values, $u$ or $l$), then $\mathrm{AppB}(x)=\ReLU(x)$.
%	
%\end{lemma}
%
%\begin{proof}
%	This is simply by definition of LP approximation functions.
%\end{proof}
%
%Notice that there is only one layer of ReLUs, in the hidden layer.
%Denote by $\mathrm{UB}$ the maximal bound on $z$ considering the MILP constraints above, with ReLUs being either linear or binary depending on whether $b \in B_{pure}$ or not.
%
%We want to show that $\mathrm{UB} = \max z$. As the MILP abstraction is a sound overapproximation, 
%it suffices to show that $\mathrm{UB}\leq \max c$.
%
%For any $b_h\in B_{pure}$, we have $b_h=\sum_{a_i\in I}w_{b_ha_i}+B_h$ ($B_h$ is the bias). 
%Denote by $B_O$ the set of nodes $b$ for which $\alpha_b$ is binary, i.e. 
%$b \notin B_{pure}$. %For any subdomain $D \subseteq B_O$, 
%Let $\boldsymbol{x}^0_J$ and $\boldsymbol{x}^0_I$ be fixed inputs, and consider the associated upper bound 
%$\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}$. We have:
%%We show that this upper bound does not exceed the maximal value of $z$: 
%
%\begin{align*}
%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} = B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)).
%\end{align*} where $\mathrm{AppB}(weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b))$ is the upper bound of 
%the (LP) approximation of $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ if $w_{b,z}>0$, and the lower bound
%of its (LP) approximation if $w_{b,z}<0$. 
%
%By Lemma \ref{lem:reach_max}, for any fixed input $\boldsymbol{x}^0_J$, for all nodes $b$ in the hidden layer, if $S(b)=\mathrm{sign}(w_{zb})=1$, then 
%$weight_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(b)$ will get its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$,
%and if $S(b)=\mathrm{sign}(w_{zb})=-1$, then $weight_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)$ will get its minimal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$.
%Notice that $\mathrm{ReLU}$ and $\mathrm{AppB}$ are both non decreasing functions, and thus:
%
%\begin{align*}
%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I} \leq B_z + \sum_{b\in B_O} w_{b,z}\ReLU(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) +
%	\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)).
%\end{align*} 
%
%Added FIX:
%Consider $B_{pure}=B^1 \cup B^2$, with $b \in B^1$ iff
%$w_{b,z} = 0$ and $b \in B^2$ iff $w_{b,z} \neq 0$.
%Hence:
%
%$$\sum_{b\in B_{pure}} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b))$$
%
%For $b \in B^2$, we have $w_{a_j,b}=0$ for all $j \in J$
%by definition of $B_{pure}$ (Lemma 4.), hence
%
%$$\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) = 
%\sum_{b\in B^2} w_{b,z} \mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))
%=\sum_{b\in B^2} w_{b,z} \mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))
%$$ as $\mathrm{AppB}(weight_{\boldsymbol{x}^*_I}(b))=\mathrm{ReLU}(weight_{\boldsymbol{x}^*_I}(b))$ since 
%$weight_{\boldsymbol{x}^*_I}(b)$ is an extremal value (minimum or maximal) and 
%$\mathrm{AppB}$ equals $\mathrm{ReLU}$ for extremal values.
%
%Hence we have: \begin{align*}
%	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}  \leq & B_z+\sum_{b}w_{zb}\ReLU(b(\boldsymbol{x}_I^*,\bar{a}_J))
%	= \max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\bar{a}_J) \\
%	\leq & \max_{\boldsymbol{x}_J}\max_{\boldsymbol{x}_I} z(\boldsymbol{x}_I,\boldsymbol{x}_J) 	= \max_{\boldsymbol{x}_K} weight_{\boldsymbol{x}_K}(z)
%\end{align*}
%
%Considering the maximal over all inputs $\boldsymbol{x}_J,\boldsymbol{x}_I$, we obtain 
%
%$$\mathrm{UB} = max_{\boldsymbol{x}_J,\boldsymbol{x}_I} \mathrm{UB}_{\boldsymbol{x}_J,\boldsymbol{x}_I} \leq \max_{\boldsymbol{x}_J,\boldsymbol{x}_I} weight_{\boldsymbol{x}_J,\boldsymbol{x}_I}(z)$$ And this us what we want to show.

\section{Proof of Theorem 2}

In this section, we will try to prove theorem 2, that is

@@

@@

	We denote $B_O$ the set of all nodes $b$ in a compensating path.
\end{lemma}

@@

	3. if $b\in B_{zero}$, then $w_{bc}=0$; otherwise there exists $<b,c,z>$ a path from $b$ to $z$ the output node with a nonzero value, a contradiction.
\end{proof}

@@

\begin{proof}
	Otherwise, suppose there exists two paths $P_1,P_2$ from $b$ to $z$ with (strictly) different signs. Then consider $\langle a_i,b\rangle+P_1$ and $\langle a_i,b\rangle+P_2$, they are two paths with weights with different signs. This is a contradiction since $a_i\in I$.
\end{proof}
Therefore, for any node $b$  that $S$ is undefined on $b$, it only depends on the values on $J$.

\begin{lemma}
	If $c$ is in the next layer of $b$, $W_{bc}\neq 0$, and $S$ is defined on both $b$ and $c$, then $W_{bc}S(c)=S(b)$.
\end{lemma}

\begin{proof}
	This is proved in the first section.
\end{proof}

@@

We denote $\boldsymbol{x}_S$ for any subset $S\subseteq K$ to refer the input vector $\langle x_{a_k}\rangle_{a_k\in S}$. We also denote $\boldsymbol{x}_I\oplus \boldsymbol{x}_J = \boldsymbol{x}_K$ and $z=z(\boldsymbol{x}_K)=z(\boldsymbol{x}_I,\boldsymbol{x}_J)$. We can see that for a node $b$ that $S$ is not defined on it, if $\boldsymbol{x}_J$ is fixed, then the value of $b$ becomes a constant.

@@

	Now, for any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers 
	as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} to get that $z(\cdot,\boldsymbol{x}^0_J)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
\end{proof}

@@

	(2) If $S(c)=1$, then we have the following:	\begin{align*}
		\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
	\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$. Now by induction hypothesis part 2, combining with $S(b)$ and both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions, we have:\begin{align*}
	\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
	&constant + \sum_{b\in B_O\cap l_i} W_{b,c}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{b,c} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
	= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
	\end{align*}  This is the first equal.
